Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-22 robdml.tex
tab
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples, which has been neglected by existing methods, can be used to
	further improve the model robustness.
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method, albeit remains
	simple, overwhelmingly outperforms the state-of-the-art defense
	methods in terms of robustness, training cost, as well as recall
	performance on benign examples.
%
\end{abstract}

@@

Such deficiency in the late training process can be alleviated with a
pseudo-hardness function that boosts the destination hardness when the loss
value is low.
%
Denoting the loss value from the previous training iteration as $\ell_{t-1}$,
we first normalize it into $[0,1]$ as $\bar{\ell}_{t-1}=\min(u,\ell_{t-1})/u$,
where $u$ is a manually specified parameter.
%
Note, $u$ is much less than the theoretical upperbound of the loss function,
in order to avoid excessive hardness boost.
%
Then the expectation of destination hardness can be linearly shifted (boosted)
by a scaled constant by a ``hardness boosting'' pseudo-hardness
function, \ie,
%
\begin{equation}
	%
	g_\mathsf{B}(H_\mathsf{D};\xi,\bar{\ell}_{t-1}) =
	H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
	%
\end{equation}
%
And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D}))$
can be used for training.

@@

@@

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the security implications of adversarial vulnerability, the
	adversarial robustness of deep metric learning models have to be improved
	via defense.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing another benign triplet or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples can further improve model robustness, which is neglected by
	previous methods.
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method overwhelmingly
	outperforms the state-of-the-art defense methods in terms of robustness,
	training cost, as well as recall performance on benign examples, while
	remains in a simple form.
%
\end{abstract}

@@

Such deficiency in the late training process can be alleviated with a
pseudo-hardness function that boosts the destination hardness when the loss
value is low.
%
Denoting the loss value from the previous training iteration as $\ell_{t-1}$,
we first normalize it into $[0,1]$ as $\bar{\ell}_{t-1}=\min(u,\ell_{t-1})/u$,
where $u$ is a manually specified parameter.
%
Note, $u$ is much less than the theoretical upperbound of the loss function,
in order to avoid excessive hardness boost in the functions introduced below.
%
Then the expectation of destination hardness can be linearly shifted (boosted)
by a scaled constant by a ``hardness boosting'' pseudo-hardness
function, \ie,
%
\begin{equation}
	%
	g_\mathsf{B}(H_\mathsf{D};\xi,\bar{\ell}_{t-1}) =
	H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
	%
\end{equation}
%
And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D}))$
can be used for training.

@@

\input{tab-ics.tex}

@@

\input{tab-sota.tex}
